### 2017-03-16 Manuscripts/cog-psych/cogpsych.tex
updates to e1, plot module

\documentclass[12pt]{article}
\usepackage[letterpaper, margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pgfplots}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage[natbibapa]{apacite}

@@

In the sections below, we present two experiments demonstrating systematic effects of category contrast on creative generation. We also introduce a novel, exemplar-based model to explain these effects: PACKER (\textit{Producing Alike and Contrasting Knowledge using Exemplar Representations}). Finally, we report formal simulations comparing PACKER to the hierarchical sampling and copy-and-tweak models developed by \cite{jern2013probabilistic}.

@@

\begin{displayquote}
As it turns out, there is another category of geometric figures called "Beta". Instead of showing you examples of the Beta category, we would like to know what you think is likely to be in the Beta category.

>>>>

\documentclass[12pt]{article}
\usepackage[letterpaper, margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pgfplots}
\usepackage{fancyhdr}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage[natbibapa]{apacite}

@@

In the sections below, we present two experiments demonstrating systematic effects of category contrast on creative generation. Our experiments conform strictly to the artificial category learning paradigm from \cite{jern2013probabilistic}: participants are first exposed to a single, experimenter-defined category, and are then asked to generate members of a new category. We also introduce a novel, exemplar-based model to explain these effects: PACKER (\textit{Producing Alike and Contrasting Knowledge using Exemplar Representations}). Finally, we report formal simulations comparing PACKER to the hierarchical sampling and copy-and-tweak models developed by \cite{jern2013probabilistic}.

To begin our investigation, we developed a artificial, two dimensional domain of squares, varying in color and size (see Figure \ref{fig:sample-stimuli} for samples). We created three unique category types within this domain, shown in Figure \ref{fig:e1-conditions}. The category types were designed to possess strong differences in the distributional structure of the experimenter-defined (`A') category, allowing us to observe the effect of category contrast under a variety of types of prior knowledge. These conditions also provide an opportunity to replicate classic effects observed in previous reports \citep[e.g.,][]{jern2013probabilistic,ward1994structured,ward2002role,marsh1999inadvertent,smith1993constraining}.

\nbcnote{This feels a little weak in motivation: how do these conditions specifically allow us to show is these effects? Did we come up with these out of thin air? So maybe foreshadow that you hardly need to look for these effects, they're \textit{everywhere}. Maybe there is also a problem that at this point it is not exactly clear what contrast means within this scenario.}

\begin{figure}
    \begin{center}
    \inputpgf{figs/}{e1-conditions.pgf}
    \caption{Category types tested in Experiment 1.}
    \label{fig:e1-conditions}
    \end{center}
\end{figure}

In the `Cluster' type, the experimenter-defined category is a tight cluster of examples in the space (e.g., all members of category `A' are small and dark in color). In the `Row' type, the category has a row pattern across the space: varying along one feature but not the other (e.g., members of category `A' are small and vary in color). In the `XOR' type, the experiment-defined category consists of two clusters separated in opposite corners of the space category, conforming to the exclusive-or logical structure (e.g., members of category `A' can be small and dark or large and light).

\begin{displayquote}
As it turns out, there is another category of geometric figures called ``Beta''. Instead of showing you examples of the Beta category, we would like to know what you think is likely to be in the Beta category.

@@
